Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-02-16 03_marlin_paper.qmd
prepping for edits on squid

@@

For this exercise, we focused on using `marlin` to assess resilience of
the selected "rule of thumb" MPA design strategies to a climate-driven
range shift. Specifically, we simulate an extreme example where the
centroid of each population shifts northward at a rate of 0.2 patches
per year, over a `r experiment_years` year time horizon (@fig-blue-ssb).
We designed MPA networks given the conditions in the starting year, and
then held that network constant over the years of the experiment,
running one simulation with and another without the climate-drive range
shift. We then compared the effects of this range shift on food
production and conservation outcomes from MPA networks designed based on
the pre-range shift world. We ran the simulation on a quarterly level ($\Delta_t = 1/4$) and set the area of each cell to an arbitrary value of 1 ($\Delta_p = 1$).

>>>>

resolution <- sqrt((coral_fauna[[1]]$patches))

@@

For this exercise, we focused on using `marlin` to assess resilience of
the selected "rule of thumb" MPA design strategies to a climate-driven
range shift. Specifically, we simulate an extreme example where the
centroid of each population shifts northward at a rate of 0.2 patches
per year, over a 20 year time horizon (@fig-blue-ssb).
We designed MPA networks given the conditions in the starting year, and
then held that network constant over the years of the experiment,
running one simulation with and another without the climate-drive range
shift. We then compared the effects of this range shift on food
production and conservation outcomes from MPA networks designed based on
the pre-range shift world. We ran the simulation on a quarterly level ($\Delta_t = 1/4$) and set the area of each cell to an arbitrary value of 1 ($\Delta_p = 1$).
